Coupling finite and boundary element methods to solve the Poisson-Boltzmann equation for electrostatics in molecular solvation

### 2023-04-26 main.tex
added link to github
minor update

\begin{figure}[h]
\centering
\colorbox{background-color}{
\fbox{
\begin{minipage}{1.0\textwidth}
\includegraphics[width=50mm,height=50mm]{graphical_abstract_fem-bem.png} %Pick only one of the two styles by uncommenting the corresponding \includegraphics
%\includegraphics[width=110mm,height=20mm]{cc.eps}
\\
    The boundary element method is, in many cases, the numerical algorithm of choice to solve the Poisson-Boltzmann equation for molecular electrostatics. However, this technique is limited to linear equations and piece-wise constant variations of the field parameters. Here, we overcome such limitations by coupling it with a finite element method, implemented using the Bempp-cl and FEniCSx libraries through simple Python interfaces. This results in an efficient, accurate, flexible, and easy-to-use computational tool for model development. 
\end{minipage}
}}
\end{figure}

@@

>>>>

\begin{figure}[h]
\centering
\colorbox{background-color}{
\fbox{
\begin{minipage}{1.0\textwidth}
\includegraphics[width=50mm,height=50mm]{graphical_abstract_fem-bem.png} %Pick only one of the two styles by uncommenting the corresponding \includegraphics
%\includegraphics[width=110mm,height=20mm]{cc.eps}
\\
    The boundary element method is a popular numerical algorithm to solve the Poisson-Boltzmann equation for molecular electrostatics. However, this technique is limited to linear equations and piece-wise constant variations of the field parameters. Here, we overcome such limitations by coupling it with a finite element method, implemented using the Bempp-cl and FEniCSx libraries through simple Python interfaces. This results in an efficient, accurate, flexible, and easy-to-use computational tool for model development. 
\end{minipage}
}}
\end{figure}

@@

\subsection*{\sffamily \large DATA AVAILABILITY STATEMENT}
All codes to reproduce the results of this manuscript can be found in the Github repository \url{https://github.com/MichalBosy/FEM_BEM_coupling/}
